---
title: "Coursera Developing Data Products"
author: "Himanshu Singh"
highlighter: highlight.js
hitheme: tomorrow
knit: slidify::knit2slides
mode: selfcontained
subtitle: Project Deck
framework: io2012
widgets: []
---

## US Rig Count Dataset Explorer  

This Shiny App is for searching and visulizating US Rig Count information from year 1987 to 2015. The total number of records is 333, seperated across Onshore, Offshore, Crude Oil and Natura Gas Rigs.
The dataset is from U.S. Energy Information Administration (http://www.eia.gov/dnav/ng/NG_ENR_DRILL_S1_M.htm).  

Data Source: http://www.eia.gov/dnav/ng/NG_ENR_DRILL_S1_M.htm  
  

--- .class #id 

# The Data for the Rig Counts
```{r echo=FALSE}
require(xlsx)
require(base64enc)
library(dplyr)
library(DT)
library(rCharts)
library(reshape)
library(knitr)
library(stats)

# Read data
data <- read.xlsx("C:/Users/RS/Documents/develp/USRigCount.xlsx", sheetName = "Aggregated", header=TRUE)
setnames(data, "Total.Rigs", "TotalNumberofRigs")
setnames(data, "Crude.Oil", "CrudeOil")
setnames(data, "Natural.Gas", "NaturalGas")
data$Year<-as.POSIXlt(data$Date)$year+1900
setnames(data, "Year", "Year")
flatdata<-melt(data[,c("Date","Year","Onshore","Offshore","CrudeOil","NaturalGas")], id=c("Date","Year"))

# Explorations and data checks
head(data)
```
# Melted Flat Dataset

```{r echo=FALSE}
head(flatdata)
```

--- .class #id 

## Total Number of Rig Counts in the US for each type

```{r echo=FALSE, comment = NA, results = "asis"}
  library(knitr)
  RigsByYear <- nPlot(
    value ~ Date,
    group = 'variable',
    data = flatdata,
    #stackedAreaChart
    #lineChart
    type = "lineChart",
    width = 900,
    hight = 400
  )
  #RigsByYear$chart(margin = list(left = 100, top = 100))
  RigsByYear$chart(color = c('purple', 'blue', 'green', 'red'))
  RigsByYear$yAxis(axisLabel = "Rig Count per Category", width = 80)
  RigsByYear$xAxis(axisLabel = "Date", width = 70)
  RigsByYear$xAxis(tickFormat ="#! function(d) {return d3.time.format('%Y/%m')(new Date(d*1000*3600*24));} !#")
  RigsByYear
```

--- .class #id 

## Total Number of Rig Counts in the US

```{r echo=FALSE, comment = NA, results = "asis"}
library(rmarkdown)
  library(knitr)
require(rCharts)
  RigsByYear <- nPlot(
    TotalNumberofRigs ~ Date,
    data = data,
    #stackedAreaChart
    #lineChart
    type = "scatterChart",
    width = 900,
    height = 400
  )
  #RigsByYear$chart(margin = list(left = 100, top = 100))
  RigsByYear$chart(color = c('purple', 'blue', 'green'))
  RigsByYear$yAxis(axisLabel = "Total Rig Count", width = 100)
  RigsByYear$xAxis(axisLabel = "Date", width = 100)
  RigsByYear$xAxis(tickFormat ="#! function(d) {return d3.time.format('%Y/%m')(new Date(d*1000*3600*24));} !#")
  RigsByYear  
```

